Ricci-Ollivier Curvature of two Random Walks on the Rooted Phylogenetic Subtree-Prune-Regraft Graph

### 2015-03-27 curvature.tex
Happy with plotting and regression.

\usepackage{amsmath,amsthm}
\usepackage{ifthen}
\usepackage{todonotes}
%\usepackage[notref,notcite]{showkeys} % show keys for eqs, etc.
\usepackage[right]{showlabels}
\usepackage{cite}
\usepackage{enumitem}
\usepackage{url}
\usepackage{subfigure}
\usepackage[nomarkers,nofiglist]{endfloat}
\let\MYoriglatexcaption\caption
\renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
% shift for todonotes
\usepackage[left=0.5in,right=1.5in,top=1in,bottom=1in,marginparwidth=1.25in]{geometry}
% regular margins
%\usepackage[margin=1in]{geometry}

@@

@@

>>>>

\usepackage{amsmath,amsthm}
\usepackage{csvsimple}
\usepackage{ifthen}
\usepackage{todonotes}
%\usepackage[notref,notcite]{showkeys} % show keys for eqs, etc.
\usepackage[right]{showlabels}
\usepackage{cite}
\usepackage{enumitem}
\usepackage{url}
\usepackage{subfigure}
\usepackage[nomarkers,nofiglist]{endfloat}
\let\MYoriglatexcaption\caption
\renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
% shift for todonotes
\usepackage[left=0.5in,right=1.5in,top=1in,bottom=1in,marginparwidth=1.25in]{geometry}
% regular margins
%\usepackage[margin=1in]{geometry}

@@

Now

@@

\begin{table}
\centering
\caption{Regression showing factors determining mean access time for rSPR.}
\subtable[5 taxa]{\csvautotabular{analysis/5-walks-200K/rspr/mean-access-5-regression.csv}}
\subtable[6 taxa]{\csvautotabular{analysis/6-walks-50K/rspr/mean-access-6-regression.csv}}
\label{TABregressionMAT}
\end{table}

\begin{table}
\centering
\caption{Regression showing factors determining $\delta_1$ for rSPR.}
\subtable[5 taxa]{\csvautotabular{analysis/5-walks-200K/rspr/delta1-5-regression.csv}}
\subtable[6 taxa]{\csvautotabular{analysis/6-walks-50K/rspr/delta1-6-regression.csv}}
\label{TABregressionDelta}
\end{table}
